Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-15 manuscript/analysis.tex

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniVsLambda.png}
\caption{The average Gini coefficient, computed before the onset of starvation,
for various values of the ER $\lambda$ connectivity parameter. 500 agents were
used in each simulation. The color band represents a bootstrapped 95\% confidence
interval.}
\label{fig:giniVsLambda}
\end{figure}

>>>>

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniVsLambda.png}
\caption{The average Gini coefficient of effective wealth (computed pre-stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income. 500 agents were used in each simulation. The color band represents a bootstrapped 95\% confidence interval.}
\label{fig:giniVsLambda}
\end{figure}
